---
title: "Exercise for Section 5.4.2"
output: learnr::tutorial
runtime: shiny_prerendered
---



```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(nycflights13)
```

## Dang
## Easy

### Exercise 1  

Find all flights that arrived on Christmas Eve (24th December)

```{r 1d, exercise=TRUE}
filter(flights, month == 12 & day == 24)
```


##  Intermediate

### Exercise 2

Find all flights with missing dep_delay, and arr_delay  

```{r 2d, exercise=TRUE}
filter(flights, is.na(dep_delay)&is.na(arr_delay))
```

## Advanced

### Exercise 3

Find all flights that belong to Mesa Airlines, Hawaiian Airlines, and Alaska Airlines

```{r 3d hint}
# type airplanes in the console
```

```{r 3d, exercise=TRUE, exercise.eval=TRUE}
filter(flights, carrier == c("YV","HA","AS"))
```

## Soujanya


## Easy 

### Question 1 

*we will be using the nycflights database in these exercises*

In the flights dataset, correct the following code so as to find the flights departed in March and April (why is it wrong?): 

```{r Correct_the_code, exercise=TRUE}
library(nycflights13)
library(tidyverse)
filter(flights, month == (3 |4 ))
```

```{r Correct_the_code-hint}
# Use infix or match operator (%in% or month == 3| month == 4)
```

## Intermediate

### Question 2

*These questions will be in parts *
Part1: Arrange flights in the order of year, month and day
Part2: Filter Delta flights departed in the month of November and December (carrier is DL)
How many rows are there now?

```{r flights, exercise=TRUE, exercise.eval=TRUE}
?flights

```

```{r flights-hint}
arrange(flights,year, month, day)
filter(flights, month %in% c(11, 12) & carrier == "DL")
nrow(filter(flights, month %in% c(11, 12) & carrier == "DL"))
```

## Challenging

### Question 3

Missing data in the flights dataset would suggest the flight being cancelled so we would prefer to remove those. Remove all the rows if there is NA in arr_delay and dep_delay.

```{r Remove_missing, exercise=TRUE, exercise.eval=TRUE}

```





