---
title: "Exercise for Section 5.4.2"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---



```{r setup, include=FALSE}
library(learnr)
library(gradethis)
tutorial_options(exercise.checker = gradethis::grade_learnr) 
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(nycflights13)
```

## Dang
## Easy

### Exercise 1  

Find all flights that arrived on Christmas Eve (24th December)



```{r 1d, exercise=TRUE}
filter(  YOU_NEED_AN_ARGUMENT_HERE  ,   YOU_NEED_AN_ARGUMENT_HERE   )
```
```{r 1d-hint-1}
"Experiment with the filter() function"

```
```{r 1d-hint-2}
"Remember that filter() takes the data set as the first argument and then some set of conditions to filter on as the second argument"

```


```{r 1d-solution }
filter(flights, month == 12 & day == 24)

```
```{r 1d-check}
gradethis::grade_code()

```


##  Intermediate

### Exercise 2

Find all flights with missing dep_delay, and arr_delay  


```{r 2d, exercise=TRUE}
filter(  YOU_NEED_AN_ARGUMENT_HERE  ,   YOU_NEED_AN_ARGUMENT_HERE   )
```
```{r 2d-hint-1}
"Experiment with the filter() function"

```
```{r 2d-hint-2}
"Remember that filter() takes the data set as the first argument and then some set of conditions to filter on as the second argument"

```


```{r 2d-solution }
filter(flights, is.na(dep_delay)&is.na(arr_delay))

```
```{r 2d-check}
gradethis::grade_code()

```
## Advanced

### Exercise 3

Find all flights that belong to Mesa Airlines, Hawaiian Airlines, and Alaska Airlines

```{r 3d hint}
# type airplanes in the console
```

```{r 3d, exercise=TRUE, exercise.eval=TRUE}
filter(flights, carrier == c("YV","HA","AS"))
```

## Soujanya


## Easy 

### Question 1 

*we will be using the nycflights database in these exercises*

In the flights dataset, correct the following code so as to find the flights departed in March and April (why is it wrong?): 

```{r Correct_the_code, exercise=TRUE}
library(nycflights13)
library(tidyverse)
filter(flights, month == (3 |4 ))
```

```{r Correct_the_code-hint}
# Use infix or match operator (%in% or month == 3| month == 4)
```

## Intermediate

### Question 2

*These questions will be in parts *
Part1: Arrange flights in the order of year, month and day
Part2: Filter Delta flights departed in the month of November and December (carrier is DL)
How many rows are there now?

```{r flights, exercise=TRUE, exercise.eval=TRUE}
?flights

```

```{r flights-hint}
arrange(flights,year, month, day)
filter(flights, month %in% c(11, 12) & carrier == "DL")
nrow(filter(flights, month %in% c(11, 12) & carrier == "DL"))
```

## Challenging

### Question 3

Missing data in the flights dataset would suggest the flight being cancelled so we would prefer to remove those. Remove all the rows if there is NA in arr_delay and dep_delay.

```{r Remove_missing, exercise=TRUE, exercise.eval=TRUE}

```


## Yuji
## Easy
### Exercise 1

In this execise, we are going to use filter(). run the code below to get the information of that. 
```{r 1, exercise=TRUE, exercise.eval=TRUE}
?filter()
```


## Intermediate
### Exercise 2

Find all flights that depart from LGA and EWR
```{r 3, exercise=TRUE, exercise.eval=TRUE}

```

## Advance
### Exercise 3

Find same flights that code below represents using !()
```{r 5, exercise=TRUE, exercise.eval=TRUE}
filter(flights, arr_delay > 60, dep_delay > 60)
```

## Easy

### question 1

Write the code to find the flights that had an arrival delay of 60 minutes or more.

```{r two-plus-two, exercise=TRUE}

```

## Moderate 

### question 2

wirte the code to find flights that departed between January and August

```{r two-plus-three, exercise=TRUE}

```

## Hard

### question 

find the flights that Departed between midnight and 7am (inclusive).

```{r two-plus-four, exercise=TRUE}

```




