---
title: "Exercise for Section 5.4.1"
output: learnr::tutorial
runtime: shiny_prerendered
---


```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(nycflights13)
```

## Dang
## Easy

### Exercise 1  

Rename air_time column to airtime 

```{r 1_d, eval=FALSE, exercise=TRUE, include=FALSE}
rename(flights, airtime=air_time)
```


##  Intermediate

### Exercise 2

Select all columns except year, month, day column  

```{r 2_d, exercise=TRUE}
select(flights, !c(year, month, day))
```

## Advanced

### Exercise 3

Select all columns not containing the word "time"

```{r 3_d, exercise=TRUE}
select(flights, !contains("time"))
```

## Yuji
## Easy
### Exercise 1

Run ?select() to learn it.
```{r 1_y, exercise=TRUE, exercise.eval=TRUE}

```

## Intermediate
### Exercise 2

Select one column on the "flights"
```{r 2_y, exercise=TRUE, exercise.eval=TRUE}

```


## Advance
### Exercise 3

Select the variable called "day" using starts_with(), ends_with(), contains().
The argument of each function must be one alphabet.

```{r 5_y, exercise=TRUE, exercise.eval=TRUE}
```


## Kamal

## Easy

### question 1

Use any_of () function to find dep_delay and dep_time vectors. Hint: use any_of(c(    )))

```{r two-plus-two, exercise=TRUE}

```

## modrate

### question 2

find the vectors dep_time, dep_delay, arr_time, arr_delay without using dep_time, dep_delay, arr_time, arr_delay in the function.

```{r two-plus-three, exercise=TRUE}

```

## Hard

### question 3

use the !! operator in a function to find the vectors of "dep_time", "dep_delay", "arr_time", "arr_delay".

```{r two-plus-four, exercise=TRUE}

```


## Soujanya
## Easy 

### Question 1 (Quiz type)

*we will be using the nycflights database in these exercises*

```{r quiz}
quiz(
  question(" The ______ operator allows you to string operations in a left-to-right fashion.",
    answer("This %<%"),
    answer("This %%%"),
    answer("This %>%", correct = TRUE),
    answer("This >%>%")
  )
)
```

```{r quiz2}
quiz(
  question(" Which of the following return a subset of the columns of a data frame?",
    answer("get"),
    answer("select", correct = TRUE),
    answer("set"),
    answer("retrieve")
  )
)
```


## Intermediate

### Question 2

*These questions will be in parts *
Part1: Make a new variable called delay which will be the total delay from departure to arrival.
Part2: Since we donot want some variables like arr_time, dep_time etc., let's drop it.

```{r flights, exercise=TRUE, exercise.eval=TRUE}
?flights

```

```{r flights-hint}
library(tidyverse)
library(nycflights13)
flights$delay <- flights$arr_delay + flights$dep_delay
select(flights, -c(arr_delay,dep_delay))
```

## Challenging

### Question 3

Let's remove all the time variables. Can we use any_of to do the same?

```{r Remove, exercise=TRUE, exercise.eval=TRUE}

```

```{r Remove-hint}
select(flights, -contains("time"))
```



